---
title: "Gender Gap in Bonus and Pay"
author: "Lyric"
date: "25/10/2021"
output: html_document
---

```{r setup,include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```



```{r, echo=FALSE, include=FALSE}
library(tidyverse)

pay17 <- read_csv("../data/UK Gender Pay Gap Data - 2017 to 2018.csv")

pay18 <- read_csv("../data/UK Gender Pay Gap Data - 2018 to 2019.csv")

pay19 <- read_csv("../data/UK Gender Pay Gap Data - 2019 to 2020.csv")

pay20 <- read_csv("../data/UK Gender Pay Gap Data - 2020 to 2021.csv")

universities <- read_csv("../data/universities.csv")

pay17 %>%
  mutate(year = "2017/18") %>%
  inner_join(universities, by = "EmployerName") %>%
  select(EmployerName, institution, year, DiffMeanHourlyPercent)  

## Now do this for all four years, store each result, and combine with rbind()

pay17year <- pay17 %>%
  mutate(year = "2017/18") %>%
  inner_join(universities, by = "EmployerName")

pay18year <- pay18 %>%
  mutate(year = "2018/19") %>%
  inner_join(universities, by = "EmployerName")

pay19year <- pay19 %>%
  mutate(year = "2019/20") %>%
  inner_join(universities, by = "EmployerName")

pay20year <- pay20 %>%
  mutate(year = "2020/21") %>%
  inner_join(universities, by = "EmployerName")


payGapData <- rbind(pay17year, pay18year, pay19year, pay20year)


```

## Bar Chart

#### The bar chart illustrates the bonus gap between genders directly.  And there is the code of this bar:

```{r code, fig.align='center',eval=TRUE}
payGapData  %>%
  select(EmployerName, MaleBonusPercent, FemaleBonusPercent, year) %>%
  group_by(year) %>%
  summarise(meanMaleBonus = mean(MaleBonusPercent),meanFemaleBonus = mean(FemaleBonusPercent))%>%
  pivot_longer(meanMaleBonus:meanFemaleBonus,
               names_to = "mean",
               values_to = "value") %>%
  ggplot(aes(x = year, y = value)) + 
  geom_bar(stat = 'identity',aes(fill = mean),position = position_dodge(0.5),width = 0.5) +
  labs(x = "Mean Bonus between male and female in a year",
       y = "meanBonusPercent")
```


##### As the bar chart show above, an increment of bonus percent can be seen in recent years.

## Table

#### The table below show the maximun, minimun, difference of max and min, mean, mean in Post-92 and mean in Pre-92 institution in 2020.



|   2020 proportion(%)  | Maximum  | Minimum  |  Diff  |  Mean | Mean in Post-92 | Mean in pre-92 |
|:-----------------------:|:--------:|:--------:|:------:|:-----:|:---------------:|:--------------:|
|     MaleBonusPercent    |   97.10  |   0.00   |  97.10 |  8.98 |       9.13      |      8.76      |
|    FemaleBonusPercent   |   98.90  |   0.00   |  98.90 |  9.67 |       9.29      |      10.20     |
|  DiffMeanHourlyPercent  |   28.20  |   3.50   |  24.70 | 14.17 |      11.80      |      17.70     |
| DiffMedianHourlyPercent |   35.00  |   0.00   |  35.00 | 13.89 |      12.70      |      15.60     |
|   DiffMeanBonusPercent  |   92.80  |  -81.80  | 174.60 | 28.10 |      11.70      |      48.4      |
|  DiffMedianBonusPercent |   92.80  |  -91.50  | 184.30 | 15.98 |       7.40      |      26.6      |

##### The table illustrates some meaningful values in divergent part and there are some hints between these values. 
##### 1. the gender gap of the pay and bonus in pre-92 institution is always greater than that of Post-92 according to the last two colomn.
##### 2. there are some inavailable data in MaleBonusPercent, FemaleBonusPercent and DiffMedianHourlyPercent cause the minimum in these parts is 0.
##### 3.the gender gap of the bonus is higher than that of the pay according to the lower four rows.
